SK500x PENGANTAR SAINS KOMPUTASI

### 2022-08-30 Semester III/Pengantar SK/Catatan Kuliah.Rmd
update

hasil %>% 
  ggplot(aes(x = t,
             y = pop)) +
  geom_line(color = "steelblue") +
  labs(title = "Hasil Simulasi Pertumbuhan Bakteri",
       subtitle = "Menggunakan Metode Beda",
       x = "Time",
       y = "Population") +
  theme_classic()
```

>>>>

hasil %>% 
  ggplot(aes(x = t,
             y = pop)) +
  geom_line(color = "steelblue") +
  labs(title = "Hasil Simulasi Pertumbuhan Bakteri",
       subtitle = "Menggunakan Metode Beda",
       x = "Time (hours)",
       y = "Population") +
  theme_classic()
```
